### 2023-02-12 oliver_copy_providence/ForArchive/sections/sims.tex
minor edits

% simulations
We use simulations to provide additional evidence for our theoretical claims regarding \Providence and to gain insight into audit behavior. As done in \cite{simulations}, we use margins from the 2020 US Presidential election---state-wide pairwise margins of $0.05$ or larger between the two leading candidates. Narrower margins are computationally expensive, especially for the simulations of tied elections, which, by design, have a low probability of stopping and hence quickly increase in sample size. We use the simulator in the R2B2 software library\cite{r2b2_anon}. For each margin, we perform $10^4$ \Providence audit trials each on a tied election (hypothesis $H_0$, the null hypothesis) and the election as reported (hypothesis $H_a$, the alternate hypothesis). All trials have risk limit $\alpha = 0.1$, a maximum of $5$ rounds, and a conditional stopping probability of $0.90$ in each round. That is, each next round size is selected to be large enough to give a $0.90$ conditional probability of stopping in that round, assuming the announced tally is correct and given the tally of previous rounds. We use a maximum of five rounds because virtually no audits would progress beyond five rounds given the large conditional probability of stopping.

@@

\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{prov_asn.png}
\caption{For the entire audit, consisting of all five rounds, the fraction of simulated audits that stopped as a function of the average number of ballots drawn for \Providence, \Minerva, EoR \BRAVO, and SO \BRAVO. The average sample number (ASN) for \B \BRAVO is included for context.}
\label{fig:prov-asn}
\end{figure}

We now investigate the efficiency of \Providence compared to \Minerva, SO \BRAVO, and EoR \BRAVO by taking a single margin as an example: the 2020 US Presidential election in the state of Texas, with margin $0.057$. We run an additional $10^4$ simulations for each of the three other audits on the same underlying election and on a tied election. Both \BRAVO implementations use a conditional stopping probability of $0.9$ for each round, while \Minerva uses a first round size with stopping probability $0.9$ and a multiplier of $1.5$ to obtain subsequent round sizes. Figure~\ref{fig:prov-asn} shows the probability of stopping as a function of the number of ballots sampled, a plot similar to those presented in \cite{simulations}. Points above (higher probability of stopping) and to the left (fewer ballots) represent more efficient audits. As shown, \Providence has comparable efficiency to \Minerva, while both are significantly more efficient than either implementation of \BRAVO. In a contest with a narrow margin (in the 2020 US Presidential election, eight states had margins smaller than $0.03$) the difference in number of ballots sampled could correspond to many days of work which would need to be completed before a certification deadline.
% Section~\ref{sec:workload} discusses workload in more depth.

>>>>

% simulations
We use simulations to provide additional evidence for our theoretical claims regarding \Providence and to gain insight into audit behavior. As done in \cite{simulations}, we use margins from the 2020 US Presidential election---state-wide pairwise margins of $0.05$ or larger between the two leading candidates. Narrower margins are computationally expensive, especially for the simulations of tied elections, which, by design, have a low probability of stopping and hence quickly increase in sample size. We use the simulator in the R2B2 software library\cite{r2b2}. For each margin, we perform $10^4$ \Providence audit trials each on a tied election (hypothesis $H_0$, the null hypothesis) and the election as reported (hypothesis $H_a$, the alternate hypothesis). All trials have risk limit $\alpha = 0.1$, a maximum of $5$ rounds, and a conditional stopping probability of $0.90$ in each round. That is, each next round size is selected to be large enough to give a $0.90$ conditional probability of stopping in that round, assuming the announced tally is correct and given the tally of previous rounds. We use a maximum of five rounds because virtually no audits would progress beyond five rounds given the large conditional probability of stopping.

@@

We now investigate the efficiency of \Providence compared to \Minerva, SO \BRAVO, and EoR \BRAVO by taking a single margin as an example: the 2020 US Presidential election in the state of Texas, with margin $0.057$. We run an additional $10^4$ simulations for each of the three other audits on the same underlying election and on a tied election. Both \BRAVO implementations use a conditional stopping probability of $0.9$ for each round, while \Minerva uses a first round size with stopping probability $0.9$ and a multiplier of $1.5$ to obtain subsequent round sizes.

\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{prov_asn.png}
\caption{For the entire audit, consisting of all five rounds, the fraction of simulated audits that stopped as a function of the average number of ballots drawn for \Providence, \Minerva, EoR \BRAVO, and SO \BRAVO. The average sample number (ASN) for \B \BRAVO is included for context.}
\label{fig:prov-asn}
\end{figure}
Figure~\ref{fig:prov-asn} shows the probability of stopping as a function of the number of ballots sampled, a plot similar to those presented in \cite{simulations}. Points above (higher probability of stopping) and to the left (fewer ballots) represent more efficient audits. As shown, \Providence has comparable efficiency to \Minerva, while both are significantly more efficient than either implementation of \BRAVO. In a contest with a narrow margin (in the 2020 US Presidential election, eight states had margins smaller than $0.03$) the difference in number of ballots sampled could correspond to many days of work which would need to be completed before a certification deadline.
% Section~\ref{sec:workload} discusses workload in more depth.

### 2023-02-12 oliver_copy_providence/ForArchive/sections/workload.tex
minor edits

\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{with_round_workload.png}
\caption{For workload parameters $w_b=1$ and $w_r=1000$, this plot shows the expected workload for various values of $p$. Expected workload is found using Equation~\ref{eq:round_workload} and the average number of ballots and rounds in our simulations as the expected number of ballots and rounds.}
\label{fig:with_round_workload}
\end{figure}

@@

\subsubsection{Precinct overhead.} For a more complete model, we can also introduce container-level workload. If a round requires multiple ballots from a single container, the container need only be unsealed once. Based on a Rhode Island pilot RLA report\cite{RI-report}, this may mean that a ballot from a new container requires roughly twice the time as a ballot from an already-opened container. Typically available election results give per-precinct granularity of vote tallies, rather than individual container information. In Virginia, however, most precincts have a single ballot scanner whose one box has sufficient capacity for all the ballots cast in that precinct anyways, and so we model the per-container workload as a per-precinct workload, $w_p$. In this model, the workload estimate incurs an additional workload of $w_p$ every time a precinct is sampled from for the first time in a round. That is, let $E_{pi}$ be the expected number of distinct precincts sampled from in round $i$, and let $E_p=\sum_i E_{pi}$. Then the new model is
\begin{equation}
W(E_b, E_r, E_p) = E_b w_b + E_r w_r + E_p w_p + C
\label{eq:round_and_precinct_workload}
\end{equation}

@@

\subsection{Real time}
Given tight certification deadlines\footnote{Virginia recently passed legislation requiring pre-certification RLAs.}, the total real time to conduct the RLA is also an important factor to consider when planning audits.
Because each county can sample ballots for the same round concurrently, the total real time for a round depends only on the slowest county. 
In Virginia, Fairfax County typically has the most votes cast by a significant difference; in the contest we consider, Fairfax County had ~551 thousand votes cast, more than double the ~203 thousand of second-highest Virginia Beach City.
Consequently, we model the expected total real time $T$ of an audit using just the largest county, and we define analagous variables for the expected values in just the largest county.
For the largest county, let the expected total ballots sampled be $\bar E_b$, the expected number of rounds $\bar E_r$, and the expected number of distinct precinct samples summed over all rounds be $\bar E_p$.
Similarly, we use real time per-ballot, per-round, and per-precinct workload variables, $t_b$, $t_r$, and $t_p$. So the real time of the audit is estimated by
\begin{equation}
T(\bar E_b, \bar E_r, \bar E_p ) = \bar E_b t_b + \bar E_r t_r + \bar E_p t_p + C
\label{eq:real_time}
\end{equation}

>>>>

\begin{figure}[h!]
\includegraphics[width=.5\textwidth]{with_round_workload.png}
\caption{For workload parameters $w_b=1$ and $w_r=1000$, this plot shows the expected workload for various round schedule parameters $p$. Expected workload is found using Equation~\ref{eq:round_workload} and the average number of ballots and rounds in our simulations as the expected number of ballots and rounds.}
\label{fig:with_round_workload}
\end{figure}

@@

\subsubsection{Precinct overhead.} For a more complete model, we can also introduce container-level workload. If. around requires multiple ballots from a single container, the container need only be unsealed once. Based on a Rhode Island pilot RLA report\cite{RI-report}, this may mean that a ballot from a new container requires roughly twice the time as a ballot from an already-opened container. Typically available election results give per-precinct granularity of vote tallies, rather than individual container information. In Virginia, however, most precincts have a single ballot scanner whose one box has sufficient capacity for all the ballots cast in that precinct anyways, and so we model the per-container workload as a per-precinct workload, $w_p$. In this model, the workload estimate incurs an additional workload of $w_p$ every time a precinct is sampled from for the first time in a round. That is, let $E_{pi}$ be the expected number of distinct precincts sampled from in round $i$, and let $E_p=\sum_i E_{pi}$. Then the new model is
\begin{equation}
W(E_b, E_r, E_p) = E_b w_b + E_r w_r + E_p w_p + C
\label{eq:round_and_precinct_workload}
\end{equation}

@@

\subsection{Real time}
Given tight certification deadlines\footnote{Virginia recently passed legislation requiring pre-certification RLAs.}, the total real time to conduct the RLA is also an important factor to consider when planning audits.
Because each county can sample ballots for the same round concurrently, the total real time for a round depends only on the slowest county. 
In Virginia, Fairfax County typically has the most votes cast by a significant difference; in the contest we consider, Fairfax County had ~551 thousand votes cast, more than double the ~203 thousand of second-highest Virginia Beach City.
Consequently, we model the expected total real time $T$ of an audit using just the largest county, and we define analagous variables for the expected values in just the largest county.
For the largest county, let the expected total ballots sampled be $\bar E_b$, the expected number of rounds $\bar E_r$, and the expected number of distinct precinct samples summed over all rounds be $\bar E_c$.
Similarly, we use real time per-ballot, per-round, and per-precinct workload variables, $t_b$, $t_r$, and $t_p$. So the real time of the audit is estimated by
\begin{equation}
T(\bar E_b, \bar E_r, \bar E_p ) = \bar E_b t_b + \bar E_r t_r + \bar E_p t_p + C
\label{eq:real_time}
\end{equation}

### 2023-02-12 oliver_copy_providence/sections/intro copy.tex
minor edits

%Intro
The literature contains numerous descriptions of vulnerabilities in deployed voting systems, and it is not possible to be certain that any system, however well-designed, will perform as expected in all instances. For this reason, 
{\em evidence-based elections} \cite{evidence-based} aim to produce trustworthy and compelling evidence of the correctness of election outcomes, enabling the detection of problems with high probability. One way to implement an evidence-based election is to use a well-curated voter-verified paper trail, compliance audits, and a rigorous tabulation audit of the election outcome, known as a risk-limiting audit (RLA) \cite{RLA}. An RLA is an audit which guarantees that the probability of concluding that an election outcome is correct, given that it is not, is below a pre-determined value known as the risk limit of the audit, independent of the true, unknown vote distribution of the underlying election. Over a dozen states in the US have seriously explored the use of RLAs---some have pilot programs, some allow RLAs to satisfy a general audit requirement and some have RLAs in statute.

This paper provides insight into the main approaches to ballot polling RLAs, the \BRAVO audit \cite{bravo}, and the newer \Minerva \cite{usenix_minerva} ballot polling RLA, through the presentation of simulation results. While some properties of the two audits may be theoretically derived, for other properties theoretical results are not available. This paper examines the number of ballots drawn over multiple rounds of both audits, for two chosen probabilities of stopping (one high: 90\%; the other low: 25\%) if the election is as announced.

\subsection{Background}
This paper focuses on ballot-polling RLAs, which require a large number of ballots relative to comparison RLAs but do not rely on any special features of the election technology. Since comparison RLAs are not always feasible, ballot-polling audits remain an important resource and have been used in a number of US state pilots (California, Georgia, Indiana, Michigan, Ohio, Pennsylvania and elsewhere). In the general ballot-polling RLA, a number of ballots are drawn and tallied in what is termed a {\em round} of ballots \cite{usenix_minerva}. A statistical measure is then computed to determine whether there is sufficient evidence to declare the election outcome correct within the pre-determined risk limit. Because the decision is made after drawing a round of ballots, the audit is termed a {\em round-by-round (R2)} audit. The special case when round size is one---that is, stopping decisions are made after each ballot draw---is a {\em ballot-by-ballot (B2)} audit.

@@

\Minerva was designed for R2 audits and applies its stopping rule once for each round. Thus it does not require the tracking of ballots that SO \BRAVO does. Zag{\'o}rski {\em et al.} \cite{usenix_minerva} prove that \Minerva is a risk-limiting audit and requires fewer ballots to be sampled than EoR \BRAVO when an audit is performed in rounds, the two audits have the same pre-determined (before any ballots are drawn) round schedule and the underlying election is as announced\footnote{Their proof assumes that the number of relevant ballots drawn in each round is know beforehand. In MINERVA, the number of ballots drawn in each round is determined before any ballots are drawn. Because invalid ballots and ballots that are inconsequential for the contest being audited would be drawn in addition to relevant ballots, the assumption used by the proof is not true in general. (We are grateful to Philip Stark for drawing our attention to this.) However, any variation in number of relevant ballots drawn for a fixed round size would be random and not chosen by an adversary; the proof showing the risk-limiting property of MINERVA could hence be extended.} . They also present first-round simulations which show that \Minerva draws fewer ballots than SO \BRAVO in the first round for first round sizes with a large probability of stopping when the (true) underlying election is as announced.

There are no results, either theoretical or based on simulations, regarding the number of ballots drawn over multiple rounds in a \Minerva audit with a pre-determined schedule. Because \BRAVO does not need to work on a pre-determined round schedule, it can optimize the size of the next round based on the sample drawn so far. Thus an open question is whether the constraint of a predetermined round schedule limits the efficacy of \Minerva in future rounds, and there is no literature comparing the number of ballots drawn by \Minerva and SO \BRAVO over multiple rounds. Note that the Average Sample Number (ASN) computations for \BRAVO \cite{bravo} apply only for B2 audits and are especially misleading as estimates of the number of ballots drawn over multiple rounds when first round sizes are large.

Both \BRAVO and \Minerva have been integrated into election audit software {\em Arlo} \cite{arlo}, and, as such, are available for use in real election audits. Both have been used in real election audits\cite{usenix_minerva, virginia_rla}. For this reason, it is important to understand their properties over multiple rounds.

\subsection{Our Contributions}
For a two candidate plurality contest with a risk limit of $10\%$, we observe the following about the total number of ballots drawn over five rounds:
\begin{enumerate}
\item Even when the first round stopping probability is as small as $0.25$, the number of ballots required for \Minerva is smaller than that required by SO \BRAVO and EoR \BRAVO. However, the improvement is considerably smaller than that when the stopping probability is $0.9$. 
\begin{itemize}
\item The number of ballots required by SO \BRAVO for a first round stopping probability of $0.9$ is about a third more than that required by \Minerva. On the other hand, for a first round stopping probability of $0.25$, it requires only about a tenth more ballots than does \Minerva.  
\item The number of ballots required by EoR \BRAVO for a first round stopping probability of $0.9$ is about twice those required by \Minerva. On the other hand, for a first round stopping probability of $0.25$, it requires only about a fourth to a half more ballots (depending on margin) than does \Minerva.  
\end{itemize}
\item For a first round stopping probability of $0.9$, when consequent \Minerva rounds are the same size (multiplying factor $1$), consequent conditional stopping probabilities are about $0.75$ and $0.74$ respectively for rounds two and three. When the multiplying factor is $1.5$, the conditional stopping probabilities for rounds two and three are $0.91$ and $0.83$ respectively. Both our simulator and the code estimating probabilities and round sizes are flexible enough to enable the study of various predetermined round schedules. 
\end{enumerate}

\subsection{Organization} Section \ref{sec:related} describes related work. The experiments we performed are described in section \ref{sec:expts}, and sections \ref{sec:results1} and \ref{sec:results2} present our results. Section \ref{sec:conc} has our conclusions.

>>>>

%Older intro file, which is mostly a repeat of the Voting paper intro 
The literature contains numerous descriptions of vulnerabilities in deployed voting systems, and it is not possible to be certain that any system, however well-designed, will perform as expected in all instances. For this reason, 
{\em evidence-based elections} \cite{evidence-based} aim to produce trustworthy and compelling evidence of the correctness of election outcomes, enabling the detection of problems with high probability. One way to implement an evidence-based election is to use a well-curated voter-verified paper trail, compliance audits, and a rigorous tabulation audit of the election outcome, known as a risk-limiting audit (RLA) \cite{RLA}. An RLA is an audit which guarantees that the probability of concluding that an election outcome is correct, given that it is not, is below a pre-determined value known as the risk limit of the audit, independent of the true, unknown vote distribution of the underlying election. Over a dozen states in the US have seriously explored the use of RLAs---some have pilot programs, some allow RLAs to satisfy a general audit requirement and some have RLAs in statute.

This paper concerns ballot-polling RLAs, which require a large number of ballots relative to comparison RLAs but do not rely on any special features of the election technology. Since comparison RLAs are not always feasible, ballot-polling audits remain an important resource and have been used in a number of US state pilots (California, Georgia, Indiana, Michigan, Ohio, Pennsylvania, Virginia and elsewhere). In the general ballot-polling RLA, a number of ballots are drawn and tallied in what is termed a {\em round} of ballots \cite{usenix_minerva}. A statistical measure is then computed to determine whether there is sufficient evidence to declare the election outcome correct within the pre-determined risk limit. If so, the audit stops; else another round is drawn. Election officials would typically decide to do a full manual hand count if the audit does not stop in spite of drawing a large number of ballots. Because the decision to stop or draw more ballots is made after drawing a round of ballots, the audit is termed a {\em round-by-round (R2)} audit. The special case when round size is one---that is, stopping decisions are made after each ballot draw---is a {\em ballot-by-ballot (B2)} audit.

@@

\Minerva was designed for R2 audits and applies its stopping rule once for each round. Thus it does not require the tracking of ballots that SO \BRAVO does. Zag{\'o}rski {\em et al.} \cite{usenix_minerva} prove that \Minerva is a risk-limiting audit and requires fewer ballots to be sampled than EoR \BRAVO when an audit is performed in rounds, the two audits have the same pre-determined (before any ballots are drawn) round schedule and the underlying election is as announced.
%\footnote{Their proof assumes that the number of relevant ballots drawn in each round is know beforehand. In MINERVA, the number of ballots drawn in each round is determined before any ballots are drawn. Because invalid ballots and ballots that are inconsequential for the contest being audited would be drawn in addition to relevant ballots, the assumption used by the proof is not true in general. (We are grateful to Philip Stark for drawing our attention to this.) However, any variation in number of relevant ballots drawn for a fixed round size would be random and not chosen by an adversary; the proof showing the risk-limiting property of MINERVA could hence be extended.}
They also present first-round simulations which show that \Minerva draws fewer ballots than SO \BRAVO in the first round for first round sizes with a large probability of stopping when the (true) underlying election is as announced. 
Broadrick {\em et al.} provide further simulations that show \Minerva requires fewer ballots over multiple rounds and for lower stopping probability.

While more efficient than \BRAVO, \Minerva requires that the round schedule is fixed in advance of the audit. This may lead to significant unnecessary work. For example, suppose the fixed round schedule for \Minerva is $10,000$ ballots per round (a reasonable number in a state-wide contest with a narrow margin), and the first round sample finds a number of ballots for the winner just short of that necessary for the audit to stop. It then may be sufficient to draw a very small second round and still stop with high probability in the second round, but the additional $10,000$ ballots must be drawn. In contrast, subsequent \BRAVO round sizes can be chosen based on preceding samples.

An open question is whether a ballot polling RLA exists with the efficiency of \Minerva and this flexibility of \BRAVO.

\subsection{Our Contributions}
We present \Providence, and provide the following:
\begin{enumerate}
\item Proof that \Providence is an RLA and resistant to an adversary who can choose subsequent round sizes with knowledge of previous samples
\item Simulations of \Providence, \Minerva, SO \BRAVO, and EoR \BRAVO which show that \Providence has similar efficiency to \Minerva, both greater than either implementation of \BRAVO
\item Results and analysis from the use of \Providence in a pilot audit in Rhode Island
\item Open source implementation of \Providence 
%including the novel metric Probability of Misleading(name?)
\end{enumerate}

%\subsection{Organization} 
%Section \ref{sec:related} describes related work. The experiments we performed are described in section \ref{sec:expts}, and sections \ref{sec:results1} and \ref{sec:results2} present our results. Section \ref{sec:conc} has our conclusions.

### 2023-02-12 oliver_copy_providence/sections/prov.tex
minor edits

@@

\subsection{Risk-Limiting Property: Proof}
\label{sec:proof}
We now prove that \Providence is risk-limiting using lemmas from basic algebra which are given in Appendix~\ref{sec:proofs}.

\begin{theorem}
\label{thm:minerva2_is_rla_new}
An $(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence audit is an
$\alpha$-RLA.
\end{theorem}
\begin{proof}
Let $\mathcal{A}=(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence.
Let $\bm{n_j}$ be the cumulative round sizes used in this
audit, with corresponding cumulative tallies of
ballots for the reported winner $\bm{k_j}$.
For round $j=1$, by Definitions \ref{def:minervatwo}
and \ref{def:minerva_ratio}, we see that
the $\mathcal{A}=\text{Correct}$ (the audit stops) only when
$$
\tau_1(k_{1},p_a,p_0,n_1)\\
=\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge \frac{1}{\alpha}.
$$
By Lemma \ref{lemma:minerva2_kmin_exists}, we see that this
is equivalent to the following:
$$
\frac{Pr[K_{1} \geq k_{min,1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{min, 1} \mid H_0, n_1]}
\ge \frac{1}{\alpha}.
$$
where $k_{min,1} = k^{p_a, p_0, \alpha, 0}_{min, 1, 0, n_1}$ (see Lemma \ref{lemma:minerva2_kmin_exists} and Definition \ref{def:kmin}).

>>>>

We now formalize these notions of weak and strong adversaries.

\begin{definition}[Weak Adversary]
A {\emph weak adversary} may choose the first round size as a function of audit parameters. That is, the first round size is a function $$n_1(\alpha, p_a, p_0).$$
\end{definition}

\begin{definition}[Strong Adversary]
A {\emph strong adversary} may choose any round size as a function of audit parameters and all precreding samples. That is, the first round size is a function 
$$n_1(\alpha, p_a, p_0),$$
and for all rounds $j\ge 2$, the round size is a function
$$n_{j+1}(\alpha, p_a, p_0, \bm{k_{j-1}}, \bm{n_{j-1}}).$$
\end{definition}

@@

\subsection{Risk-Limiting Property: Proof}
\label{sec:proof}
We now prove that \Providence is risk-limiting against a strong adversary using lemmas from basic algebra which are given in Appendix~\ref{sec:proofs}.

\begin{theorem}
\label{thm:minerva2_is_rla_new}
An $(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence audit is an
$\alpha$-RLA.
\end{theorem}
\begin{proof}
Let $\mathcal{A}=(\alpha,p_a, p_0,k_{j-1},n_{j-1},n_j)$-\Providence.
Let $\bm{n_j}$ be the cumulative round sizes used in this
audit, with corresponding cumulative tallies of
ballots for the reported winner $\bm{k_j}$.
For round $j=1$, by Definitions \ref{def:minervatwo}
and \ref{def:minerva_ratio}, we see that
the $\mathcal{A}=\text{Correct}$ (the audit stops) only when
$$
\tau_1(k_{1},p_a,p_0,n_1)\\
=\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge \frac{1}{\alpha}.
$$
By Lemma \ref{lemma:minerva2_kmin_exists} and Definition \ref{def:kmin}, there is 
a value $k_{min,1} = k^{p_a, p_0, \alpha, 0}_{min, 1, 0, n_1}$ such that 
$$
\frac{Pr[K_{1} \geq k_{1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{1} \mid H_0, n_1]}
\ge
\frac{Pr[K_{1} \geq k_{min,1} \mid H_a, n_1]}{Pr[K_{1} \geq k_{min, 1} \mid H_0, n_1]}
\ge 
\frac{1}{\alpha}.
$$

### 2023-02-12 oliver_copy_providence/sections/workload.tex
minor edits

>>>>

Importantly, note that \Minerva does not appear in the analysis in this section. 
Questions about the efficiency of \Minerva for its necessarily fixed round schedules are addressed in Section~\ref{sec:sims}, but in this section round sizes are chosen to have specified probabilities of stopping given previous samples. \Minerva is not known to be risk-limiting in this setting, and thus cannot be used for RLAs that proceed in this way.
